Coupling microsimulation models with land-use transport models

### 2019-06-11 paper.tex
Update on Overleaf.
.

Our corpus is surely not exhaustive to urban modeling as we focused on the aforementioned two main entries, and other requests such as ``urban geosimulation'', ``urban growth model'', ``urban agent based model'' would also be relevant. We expect for example, following \cite{wise2016transportation}, to have a strong overlap with our corpus and a potential corpus related to agent-based modeling. Similarly, other sub-fields of urban modeling such as cellular automata \cite{white1993cellular} or geosimulation \cite{benenson2004geosimulation} are expected to be highly interwined with our corpus from a thematic viewpoint.
%urban agent based model, spatial interaction model, spatial interaction agent based model, geosimulation, urban geosimulation, urban cellular automata, urban growth model, urban land use change model, urban land use model

@@

@@

@@

We keep the giant connected cluster of the resulting network, which covers 99.8\% of all nodes (yielding at this step $\left|V\right| = 466,610$ nodes). Inspection of removed clusters confirms that these are not relevant to urban issues (medical or chemistry microsimulations for example). Because of the way citation networks are organized and how our dataset was constructed, the full network contains a large part of ``graps'' which consist in several uncited papers citing the same one. We choose thus to work on the ``core'' of the network, which we construct by successively removing nodes of degree less or equal to one until there are no more such nodes.

@@

%%%%%%%%
\begin{figure}
    \centering
    \includegraphics{}
    \caption{}
    \label{fig:modularity-hdepth}
\end{figure}
%%%%%%%%

@@

%%%%%%%%
\begin{figure}
    \centering
    \includegraphics{figures/coveragesubnws.png}
    \caption{}
    \label{fig:coverage-hdepth}
\end{figure}
%%%%%%%%

@@

% cluster sizes
The distribution of community size is fat-tailed in a power-law manner

@@

@@

@@

%\subsection*{A case study: LUTI and microsimulation}

>>>>

Our corpus is surely not exhaustive to urban modeling as we focused on the aforementioned two main entries, and other requests such as ``urban geosimulation'', ``urban growth model'', ``urban agent based model'' would also be relevant. We expect for example, following \cite{wise2016transportation}, to have a strong overlap with our corpus and a potential corpus related to agent-based modeling. Similarly, other sub-fields of urban modeling such as cellular automata \cite{white1993cellular} or geosimulation \cite{benenson2004geosimulation} are expected to be highly intertwined with our corpus from a thematic viewpoint. To what extent these are indeed present in the corpus is an important property we will investigate.
%urban agent based model, spatial interaction model, spatial interaction agent based model, geosimulation, urban geosimulation, urban cellular automata, urban growth model, urban land use change model, urban land use model

@@

To collect bibliographic data, we follow the method introduced by \cite{raimbault2019exploration} which gathers a corpus from google scholar, and provide the open tools to do so. This source is not the best regarding metadata quality for example, but is much more exhaustive on grey literature or preprints and thus reflects the actual state of a field as it is practiced rather than a filtered and lagged in time image of it.
% remark : for some discplines / domains, this should be significantly important - I'm thinking of physics with preprints or computer science which publishes mostly in proceedings.

% TODO here introduce the horizontal depth parameter
The initial keyword requests are achieved given a parameter $h_d$ (horizontal depth), corresponding to the number of papers kept for each request. Intuitively, one could expect to retain core papers to the subject for low $h_d$ values while covering broader landscapes for high values. This will be studied with a sensitivity analysis below.

@@

The full network has a count of $\left|V\right|= 467,608$ nodes and $\left|E\right|=834,253$ citation links.

@@

We keep the giant connected cluster of the resulting network, which covers 99.8\% of all nodes.
%(yielding at this step $\left|V\right| = 466,610$ nodes).
 Inspection of removed clusters confirms that these are not relevant to urban issues (medical or chemistry microsimulations for example). Because of the way citation networks are organized and how our dataset was constructed, the full network contains a large part of ``graps'' which consist in several uncited papers citing the same one. We choose thus to work on the ``core'' of the network, which we construct by successively removing nodes of degree less or equal to one until there are no more such nodes. We finally remove manually two communities corresponding to medical science and economics of taxes papers, which appear to be connected (most probably through methodological papers) but are not relevant for our study. The final filtered network has a size of % TODO
  .

@@

%%%%%%%%
\begin{figure}
    \centering
    %\includegraphics{figures/}}}
    \caption{}
    \label{fig:modularity-hdepth}
\end{figure}
%%%%%%%%

@@

%%%%%%%%
\begin{figure}
    \centering
    \includegraphics{figures/coveragesubnws.png}
    \caption{Relative coverage of sub-networks for each initial request, as a function of horizontal depth $h_d$.}
    \label{fig:coverage-hdepth}
\end{figure}
%%%%%%%%

@@

% rq ; microsim does not appear explicitely in main title -> finally "in minority" in urban modeling ;  other terms (in case of same approach) and other approaches are preefered.

% cluster sizes
The distribution of community size is fat-tailed in a power-law manner, as scientific disciplines generally are. % TODO ref on that ?
 We can thus limit our study to the most important communities.

@@

% graph visualization and relative positioning of disciplines

We show in Fig.~\ref{fig:networkviz} a visualization of the network obtained with $h_d=3$.

% Q : what about older nws ? also show interesting entry through one kw only. - we can not visualize everything unfortunately.
%%%%%%%%
\begin{figure}
    \centering
    \includegraphics{figures/corehdepth3filteredLOWRES.png}
    \caption{Network visualization for $h_d = 3$. Node color give community obtained with the Louvain algorithm.}
    \label{fig:networkviz}
\end{figure}
%%%%%%%%

@@

\subsubsection*{A case study: LUTI, microsimulation and agent-based modeling}

% specific viz including 4 "core thematic clusters" -> abm, microsim, luti + complex systems (glue ?) [no transport abm : microsim]
% - one hypothesis (seen in temporal analysis) : complex system/complex network approaches as linking prviously less related approaches ?

@@

### 2019-06-11 wp.tex
Update on Overleaf.
.

\input{header.tex}
\begin{document}

@@

\begin{table}
\caption{Characteristics of the MATSim model}
\begin{tabular}{|c|p{6cm}|}
	\toprule
	& MATSim \\
	\midrule
Time scale & 1 day \\
Spatial scale & Any scale (mostly metropolitan area)\\
Spatial resolution & Activities coordinates \\
Agent granularity & Individual level \\
Static/Dynamic & Dynamic Stochastic User Equilibrium \\
Randomness & Stochastic co-evolutionary algorithm (agent level) \\
Process: Transportation & Several modes; microsimulated\\
Process: Economic activities & Exogenous \\
Process: Demographics & NA (agent schedules as input) \\
Process: Migration flows & NA \textbf{check if origins can change} \\
Process: Transportation congestion & Link queuing
\bottomrule
	\end{tabular}
\end{table}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Standard header for working papers
%
% WPHeader.tex
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt]{article}

%%%%%%%%%%%%%%%%%%%%%%%%%%
%% TEMPLATES
%%%%%%%%%%%%%%%%%%%%%%%%%%

% Simple Tabular

%\begin{tabular}{ |c|c|c| } 
% \hline
% cell1 & cell2 & cell3 \\ 
% cell4 & cell5 & cell6 \\ 
% cell7 & cell8 & cell9 \\ 
% \hline
%\end{tabular}

%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Packages
%%%%%%%%%%%%%%%%%%%%%%%%%%

% encoding 
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

% general packages without options
\usepackage{amsmath,amssymb,amsthm,bbm}

% graphics
\usepackage{graphicx,transparent,eso-pic}

% text formatting
\usepackage[document]{ragged2e}
\usepackage{pagecolor,color}
%\usepackage{ulem}
\usepackage{soul}

% conditions
\usepackage{ifthen}

\usepackage{booktabs}
\usepackage{threeparttable}

%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Maths environment
%%%%%%%%%%%%%%%%%%%%%%%%%%

%\newtheorem{theorem}{Theorem}[section]
%\newtheorem{lemma}[theorem]{Lemma}
%\newtheorem{proposition}[theorem]{Proposition}
%\newtheorem{corollary}[theorem]{Corollary}

%\newenvironment{proof}[1][Proof]{\begin{trivlist}
%\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
%\newenvironment{definition}[1][Definition]{\begin{trivlist}
%\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
%\newenvironment{example}[1][Example]{\begin{trivlist}
%\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
%\newenvironment{remark}[1][Remark]{\begin{trivlist}
%\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}

%\newcommand{\qed}{\nobreak \ifvmode \relax \else
%      \ifdim\lastskip<1.5em \hskip-\lastskip
%      \hskip1.5em plus0em minus0.5em \fi \nobreak
%      \vrule height0.75em width0.5em depth0.25em\fi}

%% Commands

\newcommand{\noun}[1]{\textsc{#1}}

%% Math

% Operators
\DeclareMathOperator{\Cov}{Cov}
\DeclareMathOperator{\Var}{Var}
\DeclareMathOperator{\E}{\mathbb{E}}
\DeclareMathOperator{\Proba}{\mathbb{P}}

\newcommand{\Covb}[2]{\ensuremath{\Cov\!\left[#1,#2\right]}}
\newcommand{\Eb}[1]{\ensuremath{\E\!\left[#1\right]}}
\newcommand{\Pb}[1]{\ensuremath{\Proba\!\left[#1\right]}}
\newcommand{\Varb}[1]{\ensuremath{\Var\!\left[#1\right]}}

% norm
\newcommand{\norm}[1]{\left\lVert #1 \right\rVert}

% argmin
\DeclareMathOperator*{\argmin}{\arg\!\min}

% amsthm environments
\newtheorem{definition}{Definition}
\newtheorem{proposition}{Proposition}
\newtheorem{assumption}{Assumption}

% geometry
\usepackage[margin=2cm]{geometry}

% layout : use fancyhdr package
\usepackage{fancyhdr}
\pagestyle{fancy}

\makeatletter

\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}
\fancyhead[RO,RE]{\textit{Working Paper}}
\fancyhead[LO,LE]{CASA/ISC-PIF}
\fancyfoot[RO,RE] {\thepage}
\fancyfoot[LO,LE] {\noun{J. Raimbault}}
\fancyfoot[CO,CE] {}

\makeatother

\begin{document}

@@

\begin{table}
\caption{Characteristics of the MATSim model}
\begin{tabular}{|c|p{6cm}|}
	\toprule
	& MATSim \\
	\midrule
Time scale & 1 day \\
Spatial scale & Any scale (mostly metropolitan area)\\
Spatial resolution & Activities coordinates \\
Agent granularity & Individual level \\
Static/Dynamic & Dynamic Stochastic User Equilibrium \\
Randomness & Stochastic co-evolutionary algorithm (agent level) \\
Process: Transportation & Several modes; microsimulated\\
Process: Economic activities & Exogenous \\
Process: Demographics & NA (agent schedules as input) \\
Process: Migration flows & NA \textbf{check if origins can change} \\
Process: Transportation congestion & Link queuing \\
\bottomrule
	\end{tabular}
\end{table}
